### 2019-12-03 README.Rmd
Fixed all CRAN checks
Started README

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# forestecology

The goal of forestecology is to ...

@@

``` r
# install.packages("devtools")
devtools::install_github("rudeboybert/forestecology")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```

What is special about using `README.Rmd` instead of just `README.md`? You can include R chunks like so:

```{r cars}
summary(cars)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub!

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = FALSE,
  warning = FALSE
)
```

# forestecology

[![Travis Build Status](https://travis-ci.org/rudeboybert/forestecology.svg?branch=master)](https://travis-ci.org/rudeboybert/forestecology)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/forestecology)](https://cran.r-project.org/package=forestecology)

@@

``` r
# install.packages("devtools")
devtools::install_github("rudeboybert/forestecology")
```

## Example analysis

We present an example analysis using the [Michigan Big Woods research plot
data](https://doi.org/10.7302/wx55-kt18) which is part of the Smithsonian
Institution's [Forest Global Earth Observatory
(ForestGEO)](https://forestgeo.si.edu/) global network of forest research sites.

Porting over code from `SCBI.R`

```{r, cache = TRUE}
library(tidyverse)
library(forestecology)
library(snakecase)

# Read in Big Woods census and species data
bw_2008 <- read_delim("https://deepblue.lib.umich.edu/data/downloads/z603qx485", delim = "\t") %>% 
  select(
    treeID = treeid, stemID = stemtag, sp = spcode, quadrat, gx, gy, dbh, 
    ExactDate = date, code_2008 = codes
  )
bw_2014 <- read_delim("https://deepblue.lib.umich.edu/data/downloads/1831ck00f", delim = "\t") %>% 
  select(
    treeID = treeid, stemID = stemtag, sp = spcode, quadrat, gx, gy, dbh, 
    ExactDate = date, code_2014 = codes
  )
bw_species <- read_delim("https://deepblue.lib.umich.edu/data/downloads/000000086", delim = "\t") %>% 
  mutate(spcode = to_any_case(spcode)) %>% 
  left_join(families, by = "spcode") %>% 
  mutate(
    sp = str_sub(genus, 1, 2), 
    sp = str_c(sp, str_sub(species, 1, 2)),
    sp = tolower(sp),
    latin = str_c(genus, species, sep = " ")
  ) %>% 
  select(sp, genus, species, family, latin, trait_group)
```
